oldmortality

### 2022-12-15 analyses/complexSim.Rmd
re-analyzed

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 2
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.5
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
source_python('src/getSUP.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta = 10^-7
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
layer1<-as.numeric(params$layer1)
layer2<-as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)

@@

@@

  #########################
  ###Simulate date
  #########################
  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5)))
  true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                       data = brcancer, k = 3
  ) #from flexsurv
  dat <- simsurv(betas = coefficients, # "true" parameter values
                 x = cov,                   # covariate data for 200 individuals
                 knots = true_mod$knots,    # knot locations for splines
                 logcumhazard = logcumhaz,  # definition of log cum hazard
                 maxt = 1,               # no right-censoring
                 interval = c(0,10000000)) # interval for root finding
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)

  #########################
  ###Simulate data
  #########################
  samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  data<-data[,-1]
  data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data[samp,]
  test<-data[-samp,-c(ncol(data))]
  fullTest<-data[-samp,,drop=F]
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

@@

  #########################
  ###casebase+splines
  #########################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

  glmAbsRisk<-absoluteRisk(mod_cb_glm,time=times,newdata=test,type="CI")

  glmAbsRisk<-as.data.frame(glmAbsRisk)

  rownames(glmAbsRisk)<-glmAbsRisk$time
  glmProper<- t(glmAbsRisk[-1,-1])

  class(glmProper)<-c("tunnel",class(glmProper))

  ######################
  ###PMNN splines
  ######################
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status"
  )

  fit<-fitSmoothHazSpline(pmnn,
                          epochs=epo,
                          batch_size=bsize,
                          verbose=0,
                          monitor="val_loss",
                          val_split=0.2,
                          min_delta=min_delta,
                          patience=patience)
  annPreds<-aarSplines(fit,
                       times=times,
                       x_test=test
  )
  rownames(annPreds)<-annPreds[,1]
  annProper<- t(annPreds[,-1])
  class(annProper)<-c("tunnel",class(annProper))

@@

  ######################
  ###DeepSurv
  ######################
  coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
                  num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
                  early_stopping = TRUE, epochs = epo,
                  batch_size = bsize,device = "cpu",best_weights=T,
                  patience = patience,min_delta=min_delta,batch_norm = F,
                  learning_rate = 0.001,lr_decay=10^-7)
  coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))

  ######################
  ###Deephit
  ######################
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  hitnnSurv<-t(hitnnSurv)
  colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

@@

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status"
  )

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=bsize,
                    verbose=0,
                    monitor="val_loss",
                    val_split=0.2,
                    min_delta=min_delta,
                    patience=patience)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

@@

  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'Optimal'=trueGlmProper,
                                  'PMNN_Poly'=annProperpoly),
                             #'dsm'=dsmSurvProper) ,#'dsm'=dsmCleaned,
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

@@

>>>>

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 1
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.1
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
source_python('src/getSUP.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta = 0
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
layer1<-as.numeric(params$layer1)
layer2<-as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)

@@

#########################
###Simulate date
#########################
  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5)))
  true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                       data = brcancer, k = 3
  ) #from flexsurv
  dat <- simsurv(betas = coefficients, # "true" parameter values
                 x = cov,                   # covariate data for 200 individuals
                 knots = true_mod$knots,    # knot locations for splines
                 logcumhazard = logcumhaz,  # definition of log cum hazard
                 maxt = 1,               # no right-censoring
                 interval = c(0,10000000)) # interval for root finding
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)
  data<-data[,-1]

 spec = c(train = .7, test = .1, validate = .2)

 g = sample(cut(
   seq(nrow(data)), 
   nrow(data)*cumsum(c(0,spec)),
   labels = names(spec)
 ))

 res = split(data, g)

trainOG<-res$train

test<-res$test[,-c(ncol(data))]

fullTest<-res$test

val<-res$validate

valcb<-sampleCaseBase(data = val,time="time",event="status",ratio=100)
valcb$offset<-0
valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))

numSamp<-nrow(trainOG)

@@

  #########################
  ###Simulate date
  #########################
  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5)))
  true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                       data = brcancer, k = 3
  ) #from flexsurv
  dat <- simsurv(betas = coefficients, # "true" parameter values
                 x = cov,                   # covariate data for 200 individuals
                 knots = true_mod$knots,    # knot locations for splines
                 logcumhazard = logcumhaz,  # definition of log cum hazard
                 maxt = 1,               # no right-censoring
                 interval = c(0,10000000)) # interval for root finding
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)
  data<-data[,-1]
  #########################
  ###Simulate data
  #########################
  #samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  #data<-data[,-1]
  #data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data
  #test<-data[-samp,-c(ncol(data))]
  #fullTest<-data[-samp,,drop=F]
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 100
  )
  #times<-times[-c(1,length(times))]

@@

  #########################
  ###casebase+splines
 ##########################
    mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

  glmAbsRisk<-as.data.frame(absoluteRisk(mod_cb_glm,time=times,newdata=test,type="CI"))
  rownames(glmAbsRisk)<-glmAbsRisk$time
  #prepare to run through riskRegression
  glmProper<- t(glmAbsRisk[-1,-1])
  class(glmProper)<-c("tunnel",class(glmProper))

  ######################
  ###PMNN splines
  ######################
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = 0.0001)
  )

  fit<-fitSmoothHazSpline(pmnn,
                          epochs=epo,
                          batch_size=bsize,
                          verbose=0,
                          monitor="val_loss",
                          #val_split=0.2,
                          min_delta=min_delta,
                          patience=patience,val=valcbtensor)

   annPreds<-aarSplines(fit,
                       times=times,
                       x_test=test
  )
  rownames(annPreds)<-annPreds[,1]
  annProper<- t(annPreds[,-1])
  class(annProper)<-c("tunnel",class(annProper))

@@

  source_python('src/dsurv.py')
  #need to break ties
  tiebreakTrain<-train

  #while(length(unique(tiebreakTrain$time))/length(tiebreakTrain$time)!=1 ){
  #tiebreakTrain<-train
  #tiebreakTrain$time<-tiebreakTrain$time+runif(nrow(tiebreakTrain),0,1/10000000000)
  #}

  coxnnsurv=fitDeepSurv(tiebreakTrain,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4)
  coxnnsurv<-t(coxnnsurv)
  #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

  # ######################
  # ###DeepSurv
  # ######################
  # coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
  #                 num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
  #                 early_stopping = TRUE, epochs = epo,
  #                 batch_size = bsize,device = "cpu",best_weights=T,
  #                 patience = patience,min_delta=min_delta,batch_norm = F,
  #                 learning_rate = 0.001,lr_decay=10^-7)
  # coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  # #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  # cnnCleaned<-pyProcess(coxnnsurv,times=times)
  # colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  # 
  ######################
  ###Deephit
  ######################
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=25)
  hitnnSurv<-t(hitnnSurv)
  #colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

@@

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = 0.0001)
  )

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=bsize,
                    verbose=0,
                    monitor="val_loss",
                    val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=valcbtensor)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

@@

  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'Optimal'=trueGlmProper,
                                  'PMNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

@@

  ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()+coord_cartesian(ylim=c(-1,1))

### 2022-12-15 analyses/editFreezeoldmortality.Rmd
re-analyzed

preData<-data.frame(sex=oldmort$sex,
                 civ=oldmort$civ,
                 ses=oldmort$ses.50,
                 birthplace=oldmort$birthplace,
                 ageAtDeath=oldmort$exit,
                 imrAtBirth=oldmort$imr.birth,
                 region=oldmort$region,
                 birthdate=oldmort$birthdate,
                 time=oldmort$exit-oldmort$enter,
                 status=as.numeric(oldmort$event))

preData$time<-preData$time+runif(nrow(preData),-1,1)/1000000

data<-as.data.frame((model.matrix(~.,preData)[,-1]))

#data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
covs<-colnames(data)

@@

  ######################
  ###DeepSurv
  ######################
#   a=get_pycox_activation(
#   activation = "tanh",
#   construct = TRUE,
#   alpha = 1,
#   dim = NULL,
#   lambd = 0.5,
#   min_val = -1,
#   max_val = 1,
#   negative_slope = 0.01,
#   num_parameters = 1L,
#   init = 0.25,
#   lower = 1/8,
#   upper = 1/3,
#   beta = 1,
#   threshold = 20,
#   value = 20
# )
#   coxnn<-deepsurv(formula=Surv(time, status) ~ .,data = train, frac = 0.2, activation = 'tanh',
#                   num_nodes = c(layer1,layer2), dropout = drpt,
#                   early_stopping = TRUE, epochs = epo,
#                   batch_size = bsize,device = "cpu",best_weights=T,
#                   patience = patience,min_delta=min_delta,batch_norm = T,
#                   learning_rate = 0.0001,lr_decay=10^-7)
#   coxnnsurv<- predict(coxnn,newdata = test,type="survival")
#   colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
#   cnnCleaned<-pyProcess(coxnnsurv,times=times)
#   colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))

  source_python('src/deepsurver.py')
  coxnnsurv=fitDeepSurv(train,fullTest,bsize,epochs=epo,patience=patience,min_delta=min_delta,drpt=drpt)
  coxnnsurv<-t(coxnnsurv)
  colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

  ######################
  ###Deephit
  ######################
  source_python('src/oldmortDeephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  hitnnSurv<-t(hitnnSurv)
  colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  ######################
  ###PMNN splines
  ######################
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>%layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T)%>%
    activation_tanh()%>%layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T)%>%
    activation_tanh()%>%layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)#%>%activation_tanh()

@@

  fit<-fitSmoothHazSpline(pmnn,
                          epochs=epo,
                          batch_size=5120,
                          verbose=0,
                          monitor="val_loss",
                          val_split=0.2,
                          min_delta=min_delta,
                          patience=patience)
  annPreds<-aarSplines(fit,
                       times=times,
                       x_test=test
  )
  rownames(annPreds)<-annPreds[,1]
  annProper<- t(annPreds[,-1])
  class(annProper)<-c("tunnel",class(annProper))

@@

  ######################
  ###coxph
  ######################
  cox<-coxph(Surv(time, status) ~ ., data = train,x=T)

@@

  covars_output<-covars_input%>%layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T)%>%
    activation_tanh()%>%layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T)%>%
    activation_tanh()%>%layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)#%>%activation_tanh()

@@

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=512,
                    verbose=0,
                    monitor="val_loss",
                    val_split=0.2,
                    min_delta=min_delta,
                    patience=patience)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

@@

  ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()+coord_cartesian(ylim=c(-1,0.7))
  rm(pmnn,covars_output,covars_input,fit)
  #######################
  ###Cox 
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

@@

ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=Brier,col=model))+
  geom_line()
ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()+coord_cartesian(ylim=c(-2,0.7))

>>>>

preData<-data.frame(sex=oldmort$sex,
                 civ=oldmort$civ,
                 ses=oldmort$ses.50,
                 birthplace=oldmort$birthplace,
                 ageAtEntry=oldmort$enter,
                 imrAtBirth=oldmort$imr.birth,
                 region=oldmort$region,
                 birthdate=oldmort$birthdate,
                 time=oldmort$exit-oldmort$enter,
                 status=as.numeric(oldmort$event))

#preData$time<-preData$time+runif(nrow(preData),-1,1)/1000000

data<-as.data.frame((model.matrix(~.,preData)[,-1]))
data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
covs<-colnames(data)

@@

  ######################
  ###DeepSurv
  ######################

  coxnn<-deepsurv(formula=Surv(time, status) ~ .,data = train, frac = 0.2, activation = 'selu',
                  num_nodes = c(layer1,layer2), dropout = drpt,
                  early_stopping = TRUE, epochs = epo,
                  batch_size = bsize,device = "cpu",best_weights=T,
                  patience = patience,min_delta=min_delta,batch_norm = T,
                  learning_rate = 0.0001,lr_decay=10^-7)
  coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))

  # source_python('src/deepsurver.py')
  # coxnnsurv=fitDeepSurv(train,fullTest,bsize,epochs=epo,patience=patience,min_delta=min_delta,drpt=drpt)
  # coxnnsurv<-t(coxnnsurv)
  # #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  # cnnCleaned<-pyProcess(coxnnsurv,times=times)
  # colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  # py_run_string("del fitDeepSurv")
  # rm(fitDeepSurv)

  ######################
  ###Deephit
  ######################
  source_python('src/oldmortDeephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2)
  hitnnSurv<-t(hitnnSurv)
  #colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  #colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  #######################
  ###Cox 
  ######################
  cox<-coxph(Surv(time, status) ~ ., data = train,x=T)
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

  ######################
  ###PMNN splines
  ######################
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>%
    layer_dense(units=layer1,use_bias = T)%>%
    activation_selu()%>%
    layer_batch_normalization()%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T)%>%
    activation_selu()%>%
    layer_batch_normalization()%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)#%>%activation_tanh()

@@

  fit<-fitSmoothHazSpline(pmnn,
                          epochs=epo,
                          batch_size=512,
                          verbose=0,
                          monitor="val_loss",
                          val_split=0.2,
                          min_delta=min_delta,
                          patience=patience)
  annPreds<-aarSplines(fit,
                       times=times,
                       x_test=test
  )
  rownames(annPreds)<-annPreds[,1]
  annProper<- t(annPreds[,-1])
  class(annProper)<-c("tunnel",class(annProper))

@@

@@

  covars_output<-covars_input%>%
    layer_dense(units=layer1,use_bias = T)%>%
    activation_selu()%>%
    layer_batch_normalization()%>%
    layer_dropout(drpt)%>%

    layer_dense(units=layer2,use_bias = T)%>%
    activation_selu()%>%
    layer_batch_normalization()%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)#%>%activation_tanh()

@@

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=bsize,
                    verbose=0,
                    monitor="val_loss",
                    val_split=0.2,
                    min_delta=min_delta,
                    patience=patience)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

@@

  ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()+coord_cartesian(ylim=c(-0.5,0.7))
  rm(pmnn,covars_output,covars_input,fit)

@@

ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=Brier,col=model))+
  geom_line()
ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()
